### 2019-06-03 2-Chapters/2-Chapter/chapter2.tex
Proof reading first parts of Chapter2

We give an overview of the main families of algorithms designed to tackle stochastic MAB problems, and we mainly focus on the \UCB, \klUCB{} and Thompson sampling algorithms, as they are used in the rest of the manuscript.
% We present SMPyBandits in the next Chapter~\ref{chapter:3}, a Python open-source library, designed to run numerical simulations of MAB problems, one of the main contributions of this thesis.
% We use it to compare the empirical performances of the most famous and most efficient algorithms, in terms of regret and by evaluating them on different problems.
% %
% In the point-of-view of numerical simulations or real-world applications of bandits on embedded systems, one must also take care of two other measures of performance: time and memory complexities, which can vary greatly between different families of algorithms.
% We also empirically compare different algorithms for these two measures in Section~\ref{sec:3:timeAndMemoryCosts}.
%
We then give regret upper-bounds of the two main algorithms used in this thesis, \UCB{} and \klUCB, to highlight the difference between their finite-time regret upper-bounds. They both attain a logarithmic regret, proving their order optimality (\ie, their regret upper-bound asymptotically matches the lower-bound up-to a constant factor).
% Moreover, \klUCB{} is known to be optimal for a wide range of arms distributions.
% A sketch of the proof of both results is given in Appendix.

@@

The notations used in this thesis are the usual notations in all the MAB literature, and we follow closely the formalism of \cite{Kaufmann12PhD}, as well as \cite{Slivkins2019,LattimoreBanditAlgorithmsBook,Bubeck12}.
The Nomenclature includes a summary of the notations, see Page~\pageref{chapter:nomenclature}.

@@

The most common objective for the player is to maximize its expected rewards $\E[\sum_{t=1}^T Y_t] = \sum_{t=1}^T \E[r_{A(t)}(t)]$.
The expectancy is taken on the rewards $(r_k(t))_{k,t}$, and the extern random variables $(U_s)_s$.
%
Other common objectives include best-arm identification (BAI) \cite{audibert2010best}.

\paragraph{An interactive demo to discover the MAB problem (for the novice).}
\label{par:2:interactiveDemoDiscoverMAB}
%
If you are discovering the concept of bandit model here, I would like to recommend you to go online and play a few times with an interactive demonstration.
On this demo, you will be facing a MAB problem with $K=5$ arms, and you have $T=100$ decisions to make.
The demo is hosted on my website, at \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}, and illustrated below.

@@

A bandit algorithm $\cA$, also referred to as a strategy or a policy, and sometimes denoted by $\pi$ or $\rho$, selects an arm $A(t)$ at time $t$ by using the past observations and the past external randomness.
More formally, one could state that an algorithm is a sequence of measurable functions $(\cA_t)_{t\geq1}$,
where $\cA_t$ maps the past observations $\cO_t = (U_0, Y_1, U_1, \dots, Y_{t-1}, U_{t-1})$
to an arm $\cA_t(\cO_t) = A(t) \in[K]$,
if we denote $Y_s = r_{A(s)}(s)$ the $s$-th reward.
The initial information is reduced to $\cO_1 = (U_0)$, and the first decision is $A(1) = \cA_1(\cO_1)$. Usually, most algorithms starts by selecting $A(1)=1,\dots,A(K)=K$ (or a permutation of the $K$ arms) in the $K$ first steps.
%
An algorithm is said to be deterministic if it does not depend on the external randomness $U_0,U_1,\dots$, but in this thesis we only use non-deterministic algorithms.

@@

In the example above, we consider Bernoulli distributions, but other distributions have been studied in the literature.
From now on until the last chapter of this thesis, we only consider stochastic rewards. The piece-wise stationary model is studied in Chapter~\ref{chapter:6}.
%
% Everything is implemented and documented at
% https://smpybandits.github.io/docs/Arms.html
We also focus only on real-valued rewards, meaning that $r_k(t)\in\R$ for all $k$ and $t$.

An important hypothesis is whether rewards are bounded or not,
and whether the player knows if they are bounded or not before starting the bandit game.
Moreover, if rewards are known to be bounded, let say in an interval $[a,b]$, another important hypothesis is whether the player knows the values of $a$ and $b$.
%
Intuitively, the bandit game is easier if the player knows the support of the distributions, and we restrict to this case in all the thesis.
Most of the algorithms proposed in the literature follow this hypothesis as well.
%
The mostly used
infinitely supported distributions are Gaussian, exponential and Poisson,
while in the literature, the Bernoulli distribution is the most common case of finitely supported distributions.
Continuous distributions with finite support also included truncated versions of infinitely supported distributions, in particular truncated Gaussian are used for numerical experiments in lots of research articles.

@@

-- An important result on exponential families is that \emph{a distribution in such family is entirely characterized by its parameter $\eta$}.
That is why such one-dimensional distributions are entirely characterized by their mean, as $\mu = \E_{\eta}[X]$.

-- A second important result is a simplified form for the \emph{Kullback-Leibler divergence} \cite{KullbackLeibler51}, for two distributions lying in the same exponential family.
The KL divergence is also called the relative entropy is a measure of how one probability distribution is different from a second, reference probability distribution.

@@

    Moreover, the KL divergence between $B(x)$ and $B(y)$, of parameters $\eta$, $\eta'$ is given by
    $\kl(x,y) = \KL_{B}(\eta,\eta') = x \log(x/y) + (1-x) \log((1-x)/(1-y))$.

@@

    Moreover, the KL divergence between $\cN(x,\sigma^2)$ and $\cN(x,\sigma^2)$, of parameters $\eta$, $\eta'$ is given by
    $d(x,y) = \KL_{\cN}(\eta,\eta') = (x-y)^2 / (2\sigma^2)$.
\end{itemize}

In the rest of this thesis, \emph{we only consider bounded rewards in the mathematical developments}, and we mostly focus on Bernoulli distributions, because they are usually the most relevant choice for the application of choice.
First, we restrict for simplicity to Bernoulli distributions for the simulations shown in Chapter~\ref{chapter:3}, even if our library does implement all the distributions commonly found in the literature (including unbounded one-dimensional exponential families and even Markov models).
% Then in Chapter~\ref{chapter:4}, each static IoT device in the noisy environment is assumed to be following a Bernoulli emission pattern in a fixed channel, FIXME
%
For example when we study multi-player bandits in Chapter~\ref{chapter:5}, for the model without sensing, we explain that restricting to the Bernoulli case is interesting and it is actually the hardest one, as continuous distributions with a null mass on $r(t)=0$ yield a much simpler problem.
%
Finally, in Chapter~\ref{chapter:6} we analyze our proposed algorithm in the setting on bounded distributions, without restricting to Bernoulli distributions, but we use the fact that bounded distributions on $[0,1]$ are sub-Bernoulli, and we use the Bernoulli Kullback-Leibler divergence in our analysis.

\paragraph{Other kind of hypothesis: sub-Gaussian and sub-Bernoulli distributions.}
%
A lot of research works considers rewards distributions that are not Gaussian but sub-Gaussian, of a known variance, for instance $1/4$.
For instance, bounded distributions on $[0,1]$ are known to be $1/4$ sub-Gaussian, and this fact is used for instance in \cite{Maillard2018GLR}.
It means that their moment generating function is dominated by that of a Gaussian distribution with the same mean and a variance $1/4$.
In Chapter~\ref{chapter:6}, we instead consider sub-Bernoulli distributions, formally introduced in Definition~\ref{def:6:subBernoulliDistributions}.
%
Such hypothesis is also proposed for other families of distributions, for instance \cite{KimTewari2019} analyses their Follow-the-Perturbed-Leader algorithm for perturbations following any sub-Weibull distribution (sub-Weibull distributions generalize both sub-Gaussian and sub-Exponential distributions).

\paragraph{About Markov models.}
%
% Markov models: we do not present it in this thesis.
Finally, we note that Markov models, while being implemented in SMPyBandits, are not used in this thesis.
They were introduced in the 1980s, by Whittle in \cite{Whittle1988} and Anantharam and others in \cite{Anantharam87b}.
A Markov MAB model maps an arm to a Markov chain \cite{Norris98}, instead of a distribution, and thus they are no longer stochastic nor stationary.
Such Markov models come in two flavors: rested or restless.
For $K$ arms, each Markov chain has a finite number of states $s$, each corresponding to a (constant) reward that the player obtains if she selects this arm while its Markov chain is in state $s$.
Rested Markov models means that only the state of the selected arm's Markov chain can change, following its Markov transition matrix.
Restless models remove this hypothesis, making them harder to track and solve.
%
Such models were less studied than stationary or adversarial models, but some interesting works focussed on Markov models in the last 10 years.
For instance, \cite{Melian15} proposed a cognitive radio model mixing MAB and Hidden Markov Models (HMM), solved by a mixed policy called UCB-HMM.

@@

% Other popular applications include the following.
%
% \begin{itemize}
%     \item
    \textbf{A/B testing}, for instance for websites, is a popular application of the best arm identification problem,
    where the task is purely exploratory and the player is asked to identify the best of two options (or more), in a finite number of steps \cite{audibert2010best}.
    The problem can either consider a fixed budget and no freedom on the ending of the game (\ie, an known horizon $T$), or a fixed confidence and a certain freedom on the budget (\ie, the identified arm must be the true best arm with probability at least $1-\delta$) \cite{Garivier16BAI}.
    The theoretical complexity of this use of bandit for A/B testing was first studied in \cite{Kaufmann14},
    and later on a more practical point-of-view was proposed in \cite{Jamieson17ABTest}.

@@

    % \item
    Using bandit algorithms for \textbf{improved machine learning} models or algorithms has been an active research domain for the last ten years or so.
    As presented below in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}, a certain ``leader'' bandit algorithm can be used to select on the run the best bandit algorithm from a pool of ``followers'' algorithms.
    Other possible use cases include hyper-parameter optimization, or feature selection.
    Hyper-parameters include real-valued parameters, like $\alpha\in[0,\infty)$ for the \UCB{} or $\varepsilon$ for the $\varepsilon$-greedy bandit algorithms, a step size multiplier in a gradient method, or the width of a radial based function (RBF) kernel method.
    Discrete-valued parameters are also common, like a choice in a fixed set of kernel functions or the depth of neural networks,
    and higher dimensional or more complex hyper-parameters include the entire architecture of a neural network.

@@

As explained above, the main objective of a player facing a bandit game is to maximize its (expected) cumulated reward.
An efficient algorithm should obtain a mean reward converging to the maximum reward.
We introduce in this section the notion of \emph{regret}, and the equivalence for a player between maximizing its sum of rewards and minimizing its regret.
In Machine Learning, we usually prefer to aim at minimizing certain quantities, such as the error rate in supervised learning, or the distance to the optimum in an optimization problem,
but the main interest of studying the regret is to be able to obtain higher-order information about the convergence of the mean reward to the max reward,
or in other words, to quantify the speed of convergence of a MAB algorithm.

@@

Let us first introduce some notations.
From now on, we consider a stochastic and stationary MAB problem, with $K$ arms of distributions $(\nu_k)_k$, that is, for any time $t$, $r_k(t)\sim \nu_k$.
We denote $\mu_k$ the mean of the distribution of arm $k$ (it will be referred to as the mean of arm $k$ in the rest of the manuscript), that is $\mu_k = \E[r_k(t)] \in \R$.
%
% \paragraph{Defining the regret.}
%
To define the regret, we first need to distinguish between \emph{optimal} and \emph{sub-optimal} arms.

\begin{defn}[Optimal and sub-optimal arms]\label{def:2:optimalSubOptimalArms}
    Consider a bandit problem of $K$ arms with distributions characterized by their means $\bm{\mu}=\mu_1,\dots,\mu_k$.
    Denote $\mu^* = \max_k \mu_k$ the largest mean.\\
    The best arm can be non unique, and any arm $k$ having $\mu_k = \mu^*$ is said to be \emph{optimal},
    while arms satisfying $\mu_k < \mu^*$ are called \emph{sub-optimal}.
\end{defn}

>>>>

We give an overview of the main families of algorithms designed to tackle stochastic MAB problems, and we mainly focus on the \UCB, \klUCB{} and Thompson sampling algorithms, as they are used in the rest of the manuscript.
% We present SMPyBandits in the next Chapter~\ref{chapter:3}, a Python open-source library, designed to run numerical simulations of MAB problems, one of the main contributions of this thesis.
% We use it to compare the empirical performances of the most famous and most efficient algorithms, in terms of regret and by evaluating them on different problems.
% %
% In the point-of-view of numerical simulations or real-world applications of bandits on embedded systems, one must also take care of two other measures of performance: time and memory complexities, which can vary greatly between different families of algorithms.
% We also empirically compare different algorithms for these two measures in Section~\ref{sec:3:timeAndMemoryCosts}.
%
We then give regret upper-bounds of the two main algorithms used in this thesis, \UCB{} and \klUCB, to highlight the difference between their finite-time regret upper-bounds. They both attain a logarithmic regret, proving their order optimality.
% (\ie, their regret upper-bound asymptotically matches the lower-bound up-to a constant factor).
% Moreover, \klUCB{} is known to be optimal for a wide range of arms distributions.
% A sketch of the proof of both results is given in Appendix.

@@

\paragraph{About notations.}
%
The notations used in this thesis are the usual notations in all the MAB literature, and we follow closely the formalism of \cite{Kaufmann12PhD}, as well as \cite{Slivkins2019,LattimoreBanditAlgorithmsBook,Bubeck12}.
The Nomenclature includes a summary of the notations, see Page~\pageref{chapter:nomenclature}.

@@

The most common objective for the player is to maximize its expected rewards $\E[\sum_{t=1}^T Y_t] = \sum_{t=1}^T \E[r_{A(t)}(t)]$.
The expectancy is taken on the rewards $(r_k(t))_{k,t}$, and the extern random variables $(U_s)_s$ (\ie, on the algorithm's decisions).
%
Other commonly studied objectives include best-arm identification (BAI) \cite{audibert2010best}.

\paragraph{An interactive demo to discover the MAB problem (for the novice).}
\label{par:2:interactiveDemoDiscoverMAB}
%
If you are discovering here the concept of bandits, I would like to recommend you to go online and play a few times with an interactive demonstration.
On this demo, you will be facing a MAB problem with $K=5$ arms, and you have $T=100$ decisions to make.
The demo is hosted on my website, at \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}, and it is illustrated below.

@@

A bandit algorithm $\cA$ is also referred to as a strategy or a policy, and sometimes it is denoted by $\pi$ or $\rho$ in the literature.
The algorithm $\cA$ selects an arm $A(t)$ at time $t$ by using the past observations and the past external randomness.
More formally, one could state that an algorithm is a sequence of \emph{measurable} functions $(\cA_t)_{t\geq1}$,
where $\cA_t$ maps the past observations $O_t = (U_0, Y_1, U_1, \dots, Y_{t-1}, U_{t-1})$
to an arm $\cA_t(O_t) = A(t) \in[K]$,
if we denote $Y_s = r_{A(s)}(s)$ the $s$-th reward.
The initial information is reduced to $O_1 = (U_0)$, and the first decision is $A(1) = \cA_1(O_1)$. Usually, most algorithms starts by selecting $A(1)=1,\dots,A(K)=K$ (or a permutation of the $K$ arms) in the $K$ first steps.
%
An algorithm is said to be deterministic if it does not depend on the external randomness $U_0,U_1,\dots$, but in this thesis we only use non-deterministic algorithms.

@@

In the example above, we consider Bernoulli distributions, but other distributions have been studied in the literature.
From now on until the last chapter of this thesis, we only consider stochastic rewards. The piece-wise stationary model is studied in Chapter~\ref{chapter:6}.
%
% Everything is implemented and documented at
% https://smpybandits.github.io/docs/Arms.html
We also focus only on real-valued rewards, meaning that $r_k(t)\in\R$ for all arm $k$ and time $t$.

An important hypothesis is whether rewards are bounded or not,
and whether the player knows if they are bounded or not before starting the bandit game.
Moreover, if rewards are known to be bounded, let say in an interval $[a,b]$, another important hypothesis is whether the player knows the values of $a$ and $b$ or not.
%
Intuitively, the bandit game is easier if the player knows the support of the distributions, and we restrict to this case in all the thesis, \ie, \emph{$a,b$ are always supposed to be known}.
Most of the algorithms proposed in the literature follow this hypothesis as well.
%
The mostly used
infinitely supported distributions are Gaussian, exponential and Poisson,
while in the literature, the Bernoulli distribution is the most common case of finitely supported distributions.
Continuous-valued distributions with finite support also included truncated versions of infinitely supported distributions, in particular truncated Gaussian are used for numerical experiments in lots of research articles.

@@

We have to quote two important results on exponential families:

\begin{enumerate}
    \item
    \emph{A distribution in such family is entirely characterized by its parameter $\eta$}.
    That is why one-dimensional distributions are entirely characterized by their mean, as $\mu = \E_{\eta}[X]$.

    \item
    A second important result is a simplified form for the \emph{Kullback-Leibler divergence} \cite{KullbackLeibler51}, for two distributions lying in the same exponential family.
    The KL divergence is also called the relative entropy is a measure of how one probability distribution is different from a second, reference probability distribution.
\end{enumerate}

@@

    Moreover, the KL divergence between $B(x)$ and $B(y)$, of parameters $\eta$, $\eta'$ is given by
    $\kl(x,y) = \KL_{B}(\eta,\eta') = x \log(x/y) + (1-x) \log((1-x)/(1-y))$,
    and it is also called the \emph{relative binary entropy}.

@@

    Moreover, the KL divergence between $\cN(x,\sigma^2)$ and $\cN(x,\sigma^2)$, of parameters $\eta$, $\eta'$ is given by
    $d(x,y) = \KL_{\cN,\sigma^2}(\eta,\eta') = (x-y)^2 / (2\sigma^2)$.
\end{itemize}

In the rest of this thesis, \emph{we only consider bounded rewards in the mathematical developments}, and we mostly focus on Bernoulli distributions, because they are usually the most relevant choice for the applications of choice.
First, we restrict for simplicity to Bernoulli distributions for the simulations shown in Chapter~\ref{chapter:3}, even if our library does implement all the distributions commonly found in the literature (including unbounded one-dimensional exponential families and even Markov models).
In Chapter~\ref{chapter:4}, we only study models with binary rewards.
%
Then, when we study multi-player bandits in Chapter~\ref{chapter:5}, for the model without sensing, we explain that restricting to the Bernoulli case is interesting and not restrictive, as it is actually the hardest case (since continuous distributions has a null mass on $r(t)=0$, they yield a much simpler problem as the sensing/no sensing distinction no longer makes sense).
%
Finally, in Chapter~\ref{chapter:6} we analyze our proposed algorithm in the setting on bounded distributions, without restricting to Bernoulli distributions, but we use the fact that bounded distributions on $[0,1]$ are sub-Bernoulli, and we use the Bernoulli Kullback-Leibler divergence $\kl$ in our analysis.

\paragraph{Other kind of hypothesis: sub-Gaussian and sub-Bernoulli distributions.}
%
A lot of research works considers rewards distributions that are not Gaussian but sub-Gaussian, of a known variance, for instance $1/4$.
For instance, bounded distributions on $[0,1]$ are known to be $1/4$ sub-Gaussian, and this fact is used for instance in \cite{Maillard2018GLR}.
It means that their moment generating function is dominated by that of a Gaussian distribution with the same mean and a variance $1/4$.
In Chapter~\ref{chapter:6}, we instead consider sub-Bernoulli distributions, formally introduced in Definition~\ref{def:6:subBernoulliDistributions}.
%
Such hypothesis is also proposed for other families of distributions, for instance the recent article \cite{KimTewari2019} analyses their Follow-the-Perturbed-Leader algorithm for perturbations following any sub-Weibull distribution (sub-Weibull distributions generalize both sub-Gaussian and sub-Exponential distributions).

\paragraph{About Markov models.}
%
% Markov models: we do not present it in this thesis.
Finally, we note that Markov models, while being implemented in SMPyBandits, are not used in this thesis.
They were introduced in the 1980s, by Whittle in \cite{Whittle1988} and Anantharam and others in \cite{Anantharam87b}.
A Markov MAB model maps an arm to a Markov chain \cite{Norris98}, instead of a distribution, and thus they are no longer stochastic nor stationary.
Such Markov models come in two flavors: rested or restless.
For $K$ arms, each Markov chain has a finite number of states $s$, each corresponding to a (constant) reward that the player obtains if she selects this arm while its Markov chain is in state $s$.
Rested Markov models means that only the state of the selected arm's Markov chain can change, following its Markov transition matrix.
Restless models remove this hypothesis, making them harder to track and solve.
%
Such models were less studied than stationary or adversarial models, but some interesting works focussed on Markov models in the last 10 years\footnote{~
For instance, \cite{Melian15} proposed a cognitive radio model mixing MAB and Hidden Markov Models (HMM), solved by a mixed policy called UCB-HMM.}.

@@

% Other popular applications include the following.
%
% \begin{itemize}
%     \item
    \textbf{A/B testing}, for instance for websites, is a popular application of the best arm identification problem,
    where the task is purely exploratory and the player is asked to identify the best of two options (or more), in a finite number of steps \cite{audibert2010best}.
    The problem can either consider a fixed budget and no freedom on the ending of the game (\ie, an known horizon $T$), or a fixed confidence and a certain freedom on the budget (\ie, the identified arm must be the true best arm with probability at least $1-\delta$) \cite{Garivier16BAI}.
    The theoretical complexity of this use of bandit for A/B testing was first studied in \cite{Kaufmann14},
    and a more practical point-of-view was proposed in \cite{Jamieson17ABTest}.

@@

    % \item
    Using bandit algorithms for \textbf{improved machine learning} models or algorithms has been an active research domain for the last ten years or so.
    As presented below in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}, a certain ``leader'' bandit algorithm can be used to select on the run the best bandit algorithm from a pool of ``followers'' algorithms.
    Other possible use cases include hyper-parameter optimization, or features selection.
    Hyper-parameters include real-valued parameters, like $\alpha\in[0,\infty)$ for the \UCB{} or $\varepsilon$ for the $\varepsilon$-greedy bandit algorithms, a step size multiplier in a gradient method, or the width of a radial based function (RBF) kernel method.
    Discrete-valued parameters are also common, like a choice in a fixed set of kernel functions or the depth of neural networks,
    and higher dimensional or more complex hyper-parameters can for instance be the entire architecture of a neural network.

@@

As explained above, the main objective of a player facing a bandit game is to maximize its (expected) cumulated reward.
An efficient algorithm should see its mean reward converge to the maximum reward.
We introduce in this section the notion of \emph{regret}, and the equivalence for a player between maximizing its sum of rewards and minimizing its regret.
In Machine Learning, we usually prefer to aim at minimizing certain quantities, such as the error rate in supervised learning, or the distance to the optimum in an optimization problem,
but the main interest of studying the regret is to be able to obtain higher-order information about the convergence of the mean reward to the max reward,
or in other words, to quantify the speed of convergence of a MAB algorithm.

@@

Let us first introduce some notations.
From now on, we consider a stochastic and stationary MAB problem, with $K$ arms of distributions $\nu_1,\dots,\nu_K=(\nu_k)_k$, that is, for any time $t$, $r_k(t)\sim \nu_k$.
We denote $\mu_k$ the mean of the distribution of arm $k$ (it will be referred to as the \emph{mean of arm $k$} in the rest of the manuscript), that is $\mu_k = \E[r_k(t)] \in \R$.
%
% \paragraph{Defining the regret.}
%
To define the regret, we first need to distinguish between \emph{optimal} and \emph{sub-optimal} arms.

\begin{defn}\label{def:2:optimalSubOptimalArms}
    % [Optimal and sub-optimal arms]
    Consider a bandit problem of $K$ arms with distributions characterized by their means $\bm{\mu}=\mu_1,\dots,\mu_k$.
    Denote $\mu^* = \max_k \mu_k$ the largest mean.
    The best arm can be non unique, and any arm $k$ having $\mu_k = \mu^*$ is said to be \emph{optimal},
    while arms satisfying $\mu_k < \mu^*$ are called \emph{sub-optimal}.
\end{defn}

### 2019-06-03 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Proof reading first parts of Chapter2

% FIXME
The following notations and the hypothesis on the collision information term \eqref{eq:5:collisionInformationTerm} come from Appendix~E of \cite{KaufmannAbbas19}.
Fix a player $j\in[M]$, and we consider the observations $\cO_t$ gathered by this player after $t$ rounds of its algorithm $\rho^j$:
\[ \cO_t := \left( U^j(1), Y_{A^j(1),1}, C^j(1), \ldots, U^j(t), Y_{A^j(t),t}, C^j(t) \right),\]
where $U^j(t)$ denotes some external source of randomness useful to select $A^j(t+1)$ (\eg, for an algorithm based on ranks and \UCB{} indexes, like \RhoRand, when two arms have the same maximum index, the decision is an $\argmax$ that is usually a uniform random selection among the arms with maximum index).

Fix a problem $\bm{\mu}$,
% and as we do in Appendix~\ref{proof:5:BetterLowerBound},
then introduce an alternative model parametrized by $\bm{\lambda}$, with a small difference between $\bm{\mu}$.
Fix a sub-optimal arm $k$ and $\varepsilon>0$, and $\lambda_k = \mu^*_M + \varepsilon$ and $\lambda_{\ell} = \mu_{\ell}$ for any $\ell\neq k$.
We denote $\Pr_{\bm{\mu}}^{\cO_t}$ the distribution of the vector $\cO_t$ under the model $\bm{\mu}$ when using algorithm $\rho$.
Then we introduce the \emph{collision information term} as:
\begin{equation}\label{eq:5:collisionInformationTerm}
  \cI_{\bm{\mu},\bm{\lambda}}(\rho,T) := \sum_{t=1}^{T} \mathrm{KL}(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}}, \Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}).
\end{equation}

>>>>

% FIXME
The following notations and the hypothesis on the collision information term \eqref{eq:5:collisionInformationTerm} come from Appendix~E of \cite{KaufmannAbbas19}.
Fix a player $j\in[M]$, and we consider the observations $O_t$ gathered by this player after $t$ rounds of its algorithm $\rho^j$:
\[ O_t := \left( U^j(1), Y_{A^j(1),1}, C^j(1), \ldots, U^j(t), Y_{A^j(t),t}, C^j(t) \right),\]
where $U^j(t)$ denotes some external source of randomness useful to select $A^j(t+1)$ (\eg, for an algorithm based on ranks and \UCB{} indexes, like \RhoRand, when two arms have the same maximum index, the decision is an $\argmax$ that is usually a uniform random selection among the arms with maximum index).

Fix a problem $\bm{\mu}$,
% and as we do in Appendix~\ref{proof:5:BetterLowerBound},
then introduce an alternative model parametrized by $\bm{\lambda}$, with a small difference between $\bm{\mu}$.
Fix a sub-optimal arm $k$ and $\varepsilon>0$, and $\lambda_k = \mu^*_M + \varepsilon$ and $\lambda_{\ell} = \mu_{\ell}$ for any $\ell\neq k$.
We denote $\Pr_{\bm{\mu}}^{O_t}$ the distribution of the vector $O_t$ under the model $\bm{\mu}$ when using algorithm $\rho$.
Then we introduce the \emph{collision information term} as:
\begin{equation}\label{eq:5:collisionInformationTerm}
  \cI_{\bm{\mu},\bm{\lambda}}(\rho,T) := \sum_{t=1}^{T} \mathrm{KL}(\Pr_{\bm{\mu}}^{C_t | O_{t-1}}, \Pr_{\bm{\lambda}}^{C_t | O_{t-1}}).
\end{equation}
